---
title: "rIPRscan"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{IPRscan}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Welcome to the alpha-testing phase of `riprscan`, premiered at [GLBIO 2023](https://github.com/jravilab/2023-glbio)!

Interested in running detailed a combination of evolutionary and domain architecture analyses for your protein(s) of interest? Check out our recent web-app, [MolEvolvR](http://jravilab.org/molevolvr) and associated [preprint](https://doi.org/10.1101/2022.02.18.461833) -- where we do all of these for you, and more!

## Fasta --> protein scan outputs
Users can submit a single/multifasta file (amino acid/protein sequences)
to receive detailed protein scan analyses, including match to domain profiles, localization, signal, and disorder predictions. Learn more about IPRscan [here](https://www.ebi.ac.uk/interpro/search/sequence/).


```{r submit_ipr, eval=F}
library(rinterpro)
submit_ipr(path2seq = here("inst/extdata/ex-in-CAA75348.1.faa"),
           outfolder = here("inst/extdata"),
           email = "jravilab.msu@gmail.com")
```

## Cleaning up your output data
_Coming soon!_

```{r cleanup, eval=FALSE}
cleanup_iprout(inpath='path/to/iprout', outpath='path/to/iprcln')

ipr2domarch(inpath='path/to/iprcln', outpath='path/to/ipr_da')

cleanup_domarch(prot='path/to/ipr_da',
                old = "DomArch.orig", new = "DomArch",
                domains_keep, domains_rename,
                repeat2s=TRUE, remove_tails = FALSE,
                remove_empty=F,
                domains_ignore=NULL)

```

## Visualizing your data
_Coming soon!_
```{r ipr2viz, eval=FALSE}
ipr2viz(infile_ipr = 'path/to/iprout', infile_full = 'path/to/metadata',
        accessions = c(), analysis = c("Pfam", "Phobius", "Gene3D"),
        group_by = "Analysis", topn = 20,
        name = "Name", text_size = 10, query = 'All')

```

## Questions/Feedback?
```{r q, eval=T, echo=F, background=T}
library(fontawesome)
```
-   `r fa("link", fill = "gray80")` [jravilab.github.io](https://jravilab.github.io)
-   `r fa("twitter", fill = "gray80")` [JRaviLab](https://twitter.com/jravilab)
-   `r fa("github", fill = "gray80")` [JRaviLab](https://github.com/jravilab)
-   Questions? [email us](mailto:janani.ravi@cuanschutz.edu)
